Draft

### 2024-08-16 All_tables.Rmd
Ready to knit I hope

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
library(xtable) # To have LaTeX tables based on dataframes
```

```{r}
install.packages("kableExtra")
library(kableExtra)
```

@@

```{r}
# True values
cat("True integrals are the following:\n\nNumber of trees:", nrow(trees), "\nTotal volume:", sum(trees$v), 
    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees),
    "\n\nNumber of small trees:", nrow(trees[(pi*trees$d130 < 70.5),]), "\nVolume of small trees:", sum(trees[(pi*trees$d130 < 70.5),]$v), 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]),
    "\n\nNumber of medium trees:", nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), "\nVolume of medium trees:", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]),
    "\n\nNumber of big trees:", nrow(trees[(pi*trees$d130 > 117.5),]), "\nVolume of big trees:", sum(trees[(pi*trees$d130 > 117.5),]$v), 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
    )
```

# Monte Carlo alone

@@

  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density

@@

# Bootstrap for each Monte Carlo iteration

@@

```{r}
## Nonparametric BCa
# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)
# Adapted for our particular problem
bcanon <- function(df_init,est_init,est_boot_val,p,nb_var,alpha =
                     c(.025,.975)) { 
    # df_init: initial sample
    # est_init: estimation made thanks to the initial sample
    # est_boot_val: estimations made thanks to bootstrap samples
    # p: inclusion density

@@

    # Bias-correction
    z0 <- mapply( function(j){qnorm(sum(mapply(function(long){long<est_init[,j]},est_boot_val[,j]))/nboot)} , 1:12)
    # Same as: mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)

@@

```{r}
## Making of bootstrap samples based on an initial sample
f_boot <- function(df_sample, B, nb_var){
  # df_sample: initial sample with nb_est variables and of size n; 
  # B: number of bootstrap samples made thanks to df_sample

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
  for (b in 1:B) {
    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
    # (n-1) points at random
    sample_b <- df_sample[nb,]
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*(nb_var+2)+1 + 1):(b*(nb_var+2)+1)] <- as.vector(mapply(function(j){paste("ech", b, colnames(df_sample)[j], sep = "")}, 1:(nb_var+2)))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of 4 variables and of size (n-1)
}
```

```{r}
## Making of estimations for each sample made by the bootstrap method
est_boot <- function(df, p, nb_var){
  # df: data frame with (nb_var+2)*B columns and (n-1) rows
  # p: inclusion density function (constant in the uniform case)

  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/(nb_var+2) # number of bootstrap samples
  big_est <- as.data.frame(matrix(NA, ncol = nb_var, nrow = nboot))

@@

  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
  p <- sum(rep((1/1000)*(1/1000), n))
  BOOT_df <- list() # All local variables
  BOOT_est <- list() # All estimations
  BOOT_var <- list() # Variances
  BOOT_CI <- list() # Confidence Intervals
  for (b in 1:B1) { # One MC iteration at a time
    # Uniform sampling over the whole territory
    xy <- data.frame(a1 = runif(n, 0, 1000), a2 = runif(n, 0, 1000))
    # Variables of interest derived from the sample
    all_var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
    nb_var <- length(all_var) # number of variables of interest
    df_b <- cbind(xy, all_var)

    colnames(df_b) <- paste0(raw_names, ".MC", b)[-(11:14)]
    from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
    est_b <- data.frame(from_local(1), from_local(2), from_local(3), from_local(4), from_local(5), from_local(6), from_local(7), from_local(8), 
                        (from_local(5))/(from_local(1)), (from_local(6))/(from_local(2)), 
                        (from_local(7))/(from_local(3)), (from_local(8))/(from_local(4)))
    nb_est <- length(est_b) # number of estimations
    colnames(est_b) <- paste0("est_", raw_names)[-(1:2)]

@@

@@

res1 <- MonteCarlo(n, 50)
# Just one circle to begin with

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
EST_names <- paste0("EST_", raw_names)[-(1:2)]

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
VAR_df <-

@@

```{r}
cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(unlist(VAR_nb)), "\n - for the volume of trees:", mean(unlist(VAR_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio)),
        "\n\n - for the number of small trees:", mean(unlist(VAR_nb_s)), "\n - for the volume of small trees:", mean(unlist(VAR_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_s)),
    "\n\n - for the number of medium trees:", mean(unlist(VAR_nb_m)), "\n - for the volume of medium trees:", mean(unlist(VAR_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_m)),
    "\n\n - for the number of big trees:", mean(unlist(VAR_nb_b)), "\n - for the volume of big trees:", mean(unlist(VAR_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_b)))

@@

  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
  nam_lim <- paste0("lim_", raw_names)[-(1:2)]
  CI_names <- paste0("CI_", raw_names)[-(1:2)]
  TC_names <- paste0("TC_", raw_names)[-(1:2)]
  low_names <- paste0("low_", raw_names)[-(1:2)]
  up_names <- paste0("up_", raw_names)[-(1:2)]
  length_names <- paste0("length_", raw_names)[-(1:2)]

  real_val <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
  sum(trees$v)/nrow(trees), sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
  )

@@

```{r}
# Tables
print(xtable(TC_normal, caption = "Test"))
```

```{r}
truc <- TC_normal %>%
  kable("latex", booktabs = TRUE)
truc
```

```{r}
TC_normal %>%
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major")
```

```{r}
df_total <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
PARAM_names <- c("Number of trees", "Number of small trees", "Number of medium trees", "Number of big trees", "Volume of trees", "Volume of small trees", "Volume of medium trees", "Volume of big trees", "Ratio for all trees", "Ratio for small trees", "Ratio for medium trees", "Ratio for big trees")
meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")

@@

```{r}
truc <- df_total %>%
  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

```{r}
print(truc)
```

```{r}
cat(truc)
```

@@

```{r}
diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(unlist(y)))-min(res1$Variances[x],mean(unlist(y))))/min(res1$Variances[x],mean(unlist(y)))}
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(5, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(9, VAR_ratio), "%", 
    "\n\n - for the number of small trees: ", diff_percent(2, VAR_nb_s), "%", "\n - for the volume of small trees: ", diff_percent(6, VAR_vol_s), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10, VAR_ratio_s), "%",
    "\n\n - for the number of medium trees: ", diff_percent(3, VAR_nb_m), "%", "\n - for the volume of medium trees: ", diff_percent(7, VAR_vol_m), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11, VAR_ratio_m), "%",
    "\n\n - for the number of big trees: ", diff_percent(4, VAR_nb_b), "%", "\n - for the volume of big trees: ", diff_percent(8, VAR_vol_b), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12, VAR_ratio_b), "%",
    sep = "")

@@

>>>>

```{r}
install.packages("kableExtra")
```

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
library(kableExtra) # To have LaTeX tables based on dataframes
```

@@

```{r}
# True values
real_val <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
  round(sum(trees$v)/nrow(trees), digits = 2), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 2)
  )

cat("True integrals are the following:\n\nNumber of trees:", real_val[1], "\nTotal volume:", real_val[5], 
    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val[9],
    "\n\nNumber of small trees:", real_val[2], "\nVolume of small trees:", real_val[6], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[10],
    "\n\nNumber of medium trees:", real_val[3], "\nVolume of medium trees:", real_val[7], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[11],
    "\n\nNumber of big trees:", real_val[4], "\nVolume of big trees:", real_val[8], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[12]
    )
```

```{r}
real_df <- data.frame(c("All trees", "Small trees", "Medium trees", "Big trees"), matrix(real_val, nrow = 4))
colnames(real_df) <- c("", "Number", "Volume", "Ratio Volume/Number")
```

```{r}
tab_real <- real_df %>%
  kable("latex", booktabs = TRUE, align = "lccc", linesep = c("", "\\addlinespace", "", "", "", ""), 
        caption = paste("True values proper to the database"), col.names = gsub("[.]", " ", names(real_df))) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

```{r}
# The table itself
print(tab_real)
```

```{r}
# The code that produced the table
cat(tab_real)
```

```{r}
# For each sampled point of each sample, there will be the following information:
# Coordinates, number of trees for each category, volume of trees for each category, ratios for each category
# The four categories being the whole forest, small trees, medium trees, and big trees
raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
```

# Functions

@@

  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density

@@

## Bootstrap for each Monte Carlo iteration

@@

```{r}
## Nonparametric BCa: a method to create confidence intervals
# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)
# Adapted for our particular problem
bcanon <- function(df_init,est_init,est_boot_val,p,nb_var,alpha =
                     c(.025,.975)) { 
    # df_init: initial sample
    # est_init: estimation made thanks to the initial sample
    # est_boot_val: estimations made thanks to bootstrap samples
    # p: inclusion density

@@

    # Bias-correction
    z0 <- mapply( function(j){qnorm(sum(mapply(function(long){long<est_init[,j]},est_boot_val[,j]))/nboot)} , 1:12)

@@

```{r}
## Making of bootstrap samples based on an initial sample
f_boot <- function(df_sample, B, nb_var){
  # df_sample: initial sample with nb_est variables and of size n; 
  # B: number of bootstrap samples made thanks to df_sample;
  # nb_var: number of variables of interest (for totals and not ratios)

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
  for (b in 1:B) {
    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
    # (n-1) points at random
    sample_b <- df_sample[nb,]
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*(nb_var+2)+1 + 1):(b*(nb_var+2)+1)] <- as.vector(mapply(function(j){paste("ech", b, colnames(df_sample)[j], sep = "")}, 1:(nb_var+2)))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of (nb_var+2) variables and of size (n-1)
}
```

```{r}
## Making of estimations for each sample made by the bootstrap method
est_boot <- function(df, p, nb_var){
  # df: data frame with (nb_var+2)*B columns and (n-1) rows
  # p: inclusion density function (constant in the uniform case)
  # nb_var: number of variables of interest (for totals and not ratios)

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/(nb_var+2) # number of bootstrap samples
  big_est <- as.data.frame(matrix(NA, ncol = nb_var, nrow = nboot))

@@

  p <- sum(rep((1/1000)*(1/1000), n))
  BOOT_df <- list() # All local variables
  BOOT_est <- list() # All estimations
  BOOT_var <- list() # Variances
  BOOT_CI <- list() # Confidence Intervals
  for (b in 1:B1) { # One MC iteration at a time
    # Uniform sampling over the whole territory
    xy <- data.frame(a1 = runif(n, 0, 1000), a2 = runif(n, 0, 1000))
    # Variables of interest derived from the sample
    all_var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
    nb_var <- length(all_var) # number of variables of interest
    df_b <- cbind(xy, all_var)

    colnames(df_b) <- paste0(raw_names, ".MC", b)[-(11:14)]
    from_local <- function(j){sum(df_b[2+j] /p)} # to produce HT estimators based on the sample
    est_b <- data.frame(from_local(1), from_local(2), from_local(3), from_local(4), from_local(5), from_local(6), from_local(7), from_local(8), 
                        (from_local(5))/(from_local(1)), (from_local(6))/(from_local(2)), 
                        (from_local(7))/(from_local(3)), (from_local(8))/(from_local(4)))
    nb_est <- length(est_b) # number of estimations
    colnames(est_b) <- paste0("est_", raw_names)[-(1:2)]

@@

```{r}
B0 <- 50
```

@@

res1 <- MonteCarlo(n, B0)
# Just one circle to begin with

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
EST_names <- paste0("EST_", raw_names)[-(1:2)]

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
VAR_df <- c()

@@

for (elt in res2$Variances) {
  for (j in 1:length(VAR_names)) { # For each estimation
    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
    assign(VAR_names[j], x)
  }
}

VAR_df <- c(mapply(function(j){mean(unlist(get(x = VAR_names[j])))}, 1:12))
```

```{r}
cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", VAR_df[9],
        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", VAR_df[10],
    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", VAR_df[7], "\n - for the ratio volume / number of trees:", VAR_df[11],
    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", VAR_df[8], "\n - for the ratio volume / number of trees:", VAR_df[12])

@@

  nam_lim <- paste0("lim_", raw_names)[-(1:2)]
  CI_names <- paste0("CI_", raw_names)[-(1:2)]
  TC_names <- paste0("TC_", raw_names)[-(1:2)]
  low_names <- paste0("low_", raw_names)[-(1:2)]
  up_names <- paste0("up_", raw_names)[-(1:2)]
  length_names <- paste0("length_", raw_names)[-(1:2)]

@@

```{r}
### Clean data frame to create a LaTeX table

df_total <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
PARAM_names <- c("Number of trees", "Number of small trees", "Number of medium trees", "Number of big trees", "Volume of trees", "Volume of small trees", "Volume of medium trees", "Volume of big trees", "Ratio for all trees", "Ratio for small trees", "Ratio for medium trees", "Ratio for big trees")
meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")

@@

```{r}
tab_ci <- df_total %>%
  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

```{r}
# The table itself
print(tab_ci)
```

```{r}
# The code that produced the table
cat(tab_ci)
```

@@

```{r}
diff_percent <- function(j){unlist(100*(max(res1$Variances[j],VAR_df[j])-min(res1$Variances[j],VAR_df[j]))/min(res1$Variances[j],VAR_df[j]))}
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%", 
    "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",
    "\n\n - for the number of medium trees: ", diff_percent(3), "%", "\n - for the volume of medium trees: ", diff_percent(7), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11), "%",
    "\n\n - for the number of big trees: ", diff_percent(4), "%", "\n - for the volume of big trees: ", diff_percent(8), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12), "%",
    sep = "")

@@

```{r}
# Table for comparison
diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Difference between variances` = paste0(round(mapply(function(x,y){100*(max(x,y)-min(x,y))/min(x,y)}, VAR_df, res1$Variances), digits = 3), "%") )
```

```{r}
tab_var <- diff_var %>%
  kable("latex", booktabs = TRUE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste("Comparison of the two methods when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

```{r}
# The table itself
print(tab_var)
```

```{r}
# The code that produced the table
cat(tab_var)
```

### 2024-08-16 Draft/Draft.Rmd
Ready to knit I hope

>>>>

### LaTeX tables from R data frames ----------

```{r}
library(xtable)
```

```{r}
# Tables
print(xtable(TC_normal, caption = "Test"))
```

```{r}
truc <- TC_normal %>%
  kable("latex", booktabs = TRUE)
truc
```

```{r}
TC_normal %>%
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major")
```

### Simplification of All_tables ------------

```{r}
test2 <- paste("True integrals are the following:\n\nNumber of trees:", nrow(trees), "\nTotal volume:", sum(trees$v), 
    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees),
    "\n\nNumber of small trees:", nrow(trees[(pi*trees$d130 < 70.5),]), "\nVolume of small trees:", sum(trees[(pi*trees$d130 < 70.5),]$v), 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]),
    "\n\nNumber of medium trees:", nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), "\nVolume of medium trees:", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]),
    "\n\nNumber of big trees:", nrow(trees[(pi*trees$d130 > 117.5),]), "\nVolume of big trees:", sum(trees[(pi*trees$d130 > 117.5),]$v), 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
    )
```

```{r}
cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio)),
        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_s)),
    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", mean(unlist(VAR_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_m)),
    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", mean(unlist(VAR_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_b)))

# Example:
```

```{r}
# For z0 in nonparametric BCa
# Same as: mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)
```

```{r}
# Really useless
from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
```
